A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-11 example.tex
more description

Our approach proceedings in multiple steps. Similarly as in
\cite{generate-parikh-image}, we first approximately describe each
automaton as a transition-counting flow from the initial state to its accepting
states, relating the automaton transitions to integer variables.
We use a linear integer solver to discover that some paths through the automata are incompatible
with \cref{const:more-inside-than-before,const:something-before-and-after}. This
will allow us to discover an unreachable state, which allows further
elimination. Finally, we will use case splitting to further subdivide the
problem into bite-sized products of automata, both of which are empty, thus
concluding that \cref{ex:string-constraints} is unsatisfiable.

>>>>

Our approach proceedings in multiple steps:
\begin{inparaenum}[(i)]
\item Similarly as in \cite{generate-parikh-image}, we first describe
  each automaton as a network-flow problem, counting how often each
  transition is taken in a run of the automaton.
\item   We use a linear integer solver to discover that some
  paths through the automata are incompatible with
  \cref{const:more-inside-than-before,const:something-before-and-after}. This
  will allow us to discover an unreachable state, which allows further
  elimination. Finally, we will use case splitting to further
  subdivide the problem into bite-sized products of automata, both of
  which are empty, thus concluding that \cref{ex:string-constraints}
  is unsatisfiable.
\end{inparaenum}
